Type Refinements for the Working Class

### 2015-12-24 paper.tex
fix typo

For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define
sort-indexed (resp.\ valence-indexed) copresheaves on $\SCtx$ of closed values
(resp\. bound terms) as follows:
\begin{align*}
  \ADefine{\Values_\tau(\Upsilon)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(\Upsilon)\land \exists a. \CanOperators_a(\Upsilon)\ni\vartheta
    }
  }\\
  \ADefine{
    \BTms_{v}(\Upsilon)
  }{
    \MkSet{E \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
  }
\end{align*}

>>>>

For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define
sort-indexed (resp.\ valence-indexed) copresheaves on $\SCtx$ of closed values
(resp.\ bound terms) as follows:
\begin{align*}
  \ADefine{\Values_\tau(\Upsilon)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(\Upsilon)\land \exists a. \CanOperators_a(\Upsilon)\ni\vartheta
    }
  }\\
  \ADefine{
    \BTms_{v}(\Upsilon)
  }{
    \MkSet{E \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
  }
\end{align*}
